Competing Bandits: The Perils of Exploration under Competition

### 2018-09-04 paper/content/barriers.tex
fixups
typo

\begin{finding}
\textit{Maintaining either the data or reputation advantage alone still allows the incumbent \gaedit{to retain a large share of the market compared to the share they get under permanent duopoly}.\\ \indent When the incumbent plays $\TS$, the data advantage serves as a larger barrier to entry compared to reputation, but when the incumbent plays $\DEG$ or $\DG$ there is no substantial difference between the two barriers.}
\end{finding}

>>>>

\begin{finding}
\textit{Maintaining either the data or reputation advantage alone still allows the incumbent \gaedit{to retain a larger share of the market compared to the share they get under permanent duopoly}.\\ \indent When the incumbent plays $\TS$, the data advantage serves as a larger barrier to entry compared to reputation, but when the incumbent plays $\DEG$ or $\DG$ there is no substantial difference between the two barriers.}
\end{finding}
